---
title: "Vital Signs Rwanda Yield Gap Analysis"
author: "Rachel Kenny"
date: "1/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


####Commonly Used Indicators
  # *Intercrop - ag4a_04 (1 yes/2 no)
  # *Erosion control - ag3a_14 (1 yes/2 no) ag3a_15_1, ag3a_15_2, (type: primary, secondary)
  # *Area harvested - ag4a_08
  # *Inorganic fertilizer  - ag3a_45 (1 yes/2 no), ag3a_47 (kg)
  # *Organic fertilizer  - ag3a_39 (1 yes/2 no), ag3a_40 (kg)
  # *Pesticide/herbicide - ag3a_58 (1 yes/2 no), ag3a_59 {1: 'Pesticide', 2: 'Herbicide', 3:  'Fungicide'}, ag3a_60_1 (kg), pesticide_kg, herbicide_kg, fungicide_kg

```{r}

#load libraries
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(broom)
library(purrr)
library(dotwhisker)
library(estimatr)
library(readr)
library(RColorBrewer)
library(wesanderson)

#load data
fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season_fieldcrop.csv"))
hh_fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_fieldcrop.csv"))
field_season <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season.csv"))
hh_indiv <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_individual.csv"))

#View(household_field_season_fieldcrop)
```


```{r}
#Filter fieldcrop, treat factors as factors and numeric as numeric
fieldcrop <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15 != "na")
fieldcrop$ag4a_08 <- as.numeric(fieldcrop$ag4a_08)
fieldcrop$ag4a_15 <- as.numeric(fieldcrop$ag4a_15)
fieldcrop$ag4a_15_unit <- as.factor(fieldcrop$ag4a_15_unit)
fieldcrop$crop_name <- as.factor(fieldcrop$crop_name)
fieldcrop$ag4a_15_unit[which(fieldcrop$ag4a_15_unit=="Liter")] <- "Kg" #because this is a misentry
fieldcrop <- filter(fieldcrop, ag4a_15_unit == "Kg")

#fix crop name mismatches
fieldcrop$crop_name[which(fieldcrop$crop_name=="Irish potatoes")] <- "Irish Potatoes"
fieldcrop$crop_name[which(fieldcrop$crop_name=="Blood fruit")] <- "Blood Fruit"  

#Filter field_season, treat factors as factors and numeric as numeric
field_season <- filter(field_season, country == 'RWA',  ag3a_03 == 'Cultivated' )
field_season$ag3a_39 <- as.factor(field_season$ag3a_39)
field_season$ag3a_39a <- as.factor(field_season$ag3a_39a)
field_season$ag3a_39a_other <- as.factor(field_season$ag3a_39a_other)
field_season$ag3a_40 <- as.numeric(field_season$ag3a_40)
field_season$ag3a_45 <- as.factor(field_season$ag3a_45)
field_season$ag3a_47 <- as.factor(field_season$ag3a_47)

#fix crop name mismatch
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Irish potatoes")] <- "Irish Potatoes"
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Blood fruit")] <- "Blood Fruit"

#fset landscape # as factor in household survey data
hh_fieldcrop$landscape_no <- as.factor(hh_fieldcrop$landscape_no)

#Join fieldcrop and field_season dataframes
joined_df <- inner_join(field_season, fieldcrop, by =c("id"= "parent_id", 'round', "landscape_no", "country", "field_no", "hh_refno", "season"))

#Add columns for yield
joined_df <- mutate(joined_df, kg_peracre = ag4a_15/ag4a_08)
joined_df <- mutate(joined_df, kg_perha = kg_peracre*(1/.404686))

#per acre planted 
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/4")] <- .25
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/2")] <- .5
joined_df$ag4a_02[which(joined_df$ag4a_02=="3/4")] <- .75
joined_df$ag4a_02[which(joined_df$ag4a_02=="Almost All")] <- 1
joined_df$ag3a_40 <- as.numeric(joined_df$ag3a_40)
joined_df$ag3a_47 <- as.numeric(joined_df$ag3a_47)
joined_df$ag4a_02 <- as.numeric(joined_df$ag4a_02)

joined_df <- mutate(joined_df, kg_peracre_planted = case_when(ag4a_01 == TRUE ~ kg_peracre, ag4a_01 == FALSE ~ ag4a_15/(ag4a_08*ag4a_02))) %>% 
  mutate(kg_perha_planted = kg_peracre_planted *(1/.404686))

#value per hectare planted 
joined_df <- filter(joined_df, kg_perha_planted != Inf) %>% 
  mutate(value_peracre = ag4a_16/ag4a_08) %>% 
  mutate(value_perha = value_peracre*(1/.404686)) %>% 
  mutate(value_peracre_planted = case_when(ag4a_01 == TRUE ~ value_peracre, ag4a_01 == FALSE ~ ag4a_16/ag4a_08*ag4a_02)) %>% 
  mutate(value_perha_planted = value_peracre_planted *(1/.404686))


#Add column for pesticide kg per hectare planted
joined_df <-mutate(joined_df, pesticide_use_kg = ifelse(ag3a_60_2 == "Millilitre", ag3a_60_1*0.001, ag3a_60_1)) %>% 
  mutate(pesticide_use_kg = case_when(ag3a_58 == TRUE ~ pesticide_use_kg, ag3a_58 == FALSE ~ 0)) %>% 
  mutate(pest_peracre = pesticide_use_kg/ag4a_08) %>% 
  mutate(pest_perha = pest_peracre*(1/.404686)) %>% 
  mutate(pest_peracre_planted = case_when(ag4a_01 == TRUE ~ pest_peracre, ag4a_01 == FALSE ~ pest_peracre/ag4a_02)) %>% 
  mutate(pest_perha_planted = pest_peracre_planted *(1/.404686))

#Add column for inorg fert kg per hectare planted
joined_df <- mutate(joined_df, inorg_peracre = ag3a_47/ag4a_08) %>% 
  mutate(inorg_perha = inorg_peracre*(1/.404686)) %>%  
  mutate(inorg_perha_planted = case_when(ag4a_01 == TRUE ~ inorg_perha, ag4a_01 == FALSE ~ inorg_perha/ag4a_02)) %>% 
  mutate(inorg_perha_planted = case_when(ag3a_45 ==TRUE ~ inorg_perha_planted, ag3a_45 == FALSE ~ 0 ))

#Add column for org fert kg per hectare planted
joined_df <- mutate(joined_df, org_peracre = ag3a_40/ag4a_08) %>% 
  mutate(org_perha = org_peracre*(1/.404686)) %>%
  mutate(org_perha_planted = case_when(ag4a_01 == TRUE ~ org_peracre, ag4a_01 == FALSE ~ org_perha/ag4a_02)) %>% 
  mutate(org_perha_planted = case_when(ag3a_39 ==TRUE ~ org_perha_planted, ag3a_39 == FALSE ~ 0 ))

#Summarize number of entries per crop
joined_df %>%
  group_by(crop_name) %>%
  tally()

#subset data n>30, reveals top 10 plots
jdf_n30 <- filter(joined_df, crop_name == "Banana Beer" | crop_name == "Banana Food" | crop_name == "Beans" | crop_name == "Cassava" | crop_name == "Field Peas" | crop_name == "Groundnut" | crop_name == "Irish Potatoes" | crop_name == "Maize" | crop_name == "Paddy" | crop_name == "Pyrethrum" | crop_name == "Sorghum" | crop_name == "Soyabeans" | crop_name == "Sweet Potatoes" | crop_name == "Wheat")

```


```{r}

cr <- unique(jdf_n30$crop_name)

jdf_n30 <- jdf_n30[!is.na(jdf_n30$ag4a_04),] #Removes NA value for intercropping

#create exclude variable
jdf_n30$exclude_1 <- NA
jdf_n30$exclude_2.5 <- NA
jdf_n30$exclude_5 <- NA

for(i in 1:length(cr)){
jdf_n30$exclude_1[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.99) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.01), 1, 0)

jdf_n30$exclude_2.5[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.975) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.025), 1, 0)
    
jdf_n30$exclude_5[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.95) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.05), 1, 0)
}

table(jdf_n30$exclude_1, useNA="always")
table(jdf_n30$exclude_2.5, useNA="always")
table(jdf_n30$exclude_5, useNA="always")

jdf_n30_1 <- jdf_n30[jdf_n30$exclude_1==0,]
jdf_n30_2.5 <- jdf_n30[jdf_n30$exclude_2.5==0,]
jdf_n30_5 <- jdf_n30[jdf_n30$exclude_5==0,]

#create yield gap variable 
dta <- list(jdf_n30_1, jdf_n30_2.5, jdf_n30_5)
for(i in 1:length(dta)){
  for(j in 1:length(cr)){
    dta[[i]]$yield_gap[dta[[i]]$crop_name==cr[j]] <- ifelse(dta[[i]]$kg_perha_planted[dta[[i]]$crop_name==cr[j]] > quantile(dta[[i]]$kg_perha_planted[dta[[i]]$crop_name==cr[j]], probs=0.75), 1, 0)
  }
}
#table(dta[[1]]$yield_gap, useNA="always") #code to check number of entries
```

####T-tests
Yield ~ Intercrop
```{r}
#yield_intercrop_tt-tests
yield_intercrop_ttests_1 <- list()
yield_intercrop_ttests_2.5 <- list()
yield_intercrop_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag4a_04, useNA="always")


keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans",  "Banana Food", "Field Peas", "Groundnut", "Sweet Potatoes")

#t-test of yield ~ intercrop (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df,
               alternative="greater")
  yield_intercrop_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df1,
               alternative="greater")
  yield_intercrop_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df2,
               alternative="greater")
  yield_intercrop_ttests_5[[i]] <- stat5
}

#yield_intercrop_tt-tests
yield_intercrop_ttests_1 
yield_intercrop_ttests_2.5 
yield_intercrop_ttests_5 

#yield_intercrop_table <- map_df(yield_intercrop_ttests_5, tidy)
#names(yield_intercrop_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
#yield_intercrop_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]

```

####T-tests Yield
Yield ~ Pesticide
```{r}
#yield_pesticide_tt-tests
yield_pesticide_ttests_1 <- list()
yield_pesticide_ttests_2.5 <- list()
yield_pesticide_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")


keep <- c("Beans", "Irish Potatoes", "Maize", "Paddy")

#t-test of yield ~ pesticide (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df,
               alternative="greater")
  yield_pesticide_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df1,
               alternative="greater")
  yield_pesticide_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df2,
               alternative="greater")
  yield_pesticide_ttests_5[[i]] <- stat5
}

#yield_pesticide_tt-tests
yield_pesticide_ttests_1 
yield_pesticide_ttests_2.5 
yield_pesticide_ttests_5 

#yield_pesticide_table <- map_df(yield_pesticide_ttests_5, tidy)
#names(yield_pesticide_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
#yield_pesticide_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```


Yield ~ Organic Fertilizer
```{r}
#yield_org_tt-tests
yield_org_ttests_1 <- list()
yield_org_ttests_2.5 <- list()
yield_org_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_39, useNA="always")


keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")

#t-test of yield ~ organic fertilizer (yes/no) 
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df,
               alternative="greater")
  yield_org_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df1,
               alternative="greater")
  yield_org_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df2,
               alternative="greater")
  yield_org_ttests_5[[i]] <- stat5
}

#yield_org_tt-tests
yield_org_ttests_1 
yield_org_ttests_2.5 
yield_org_ttests_5 

#yield_org_table <- map_df(yield_org_ttests_2.5, tidy)
#names(yield_org_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
#yield_org_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```

Yield ~ Inorganic Fertilizer
```{r}
#yield_inorg_tt-tests
yield_inorg_ttests_1 <- list()
yield_inorg_ttests_2.5 <- list()
yield_inorg_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_45, useNA="always")
table(joined_df$crop_name, joined_df$ag3a_45, useNA="always")

keep <- c("Beans", "Irish Potatoes", "Maize", "Wheat")

#t-test of yield ~ inorg (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df,
               alternative="greater")
  yield_inorg_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df1,
               alternative="greater")
  yield_inorg_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df2,
               alternative="greater")
  yield_inorg_ttests_5[[i]] <- stat5
}

#yield_inorg_tt-tests
yield_inorg_ttests_1 
yield_inorg_ttests_2.5 
yield_inorg_ttests_5 

# yield_inorg_table <- map_df(yield_inorg_ttests_2.5, tidy)
# names(yield_inorg_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
# yield_inorg_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```



####YIELD AS A FUNCTION OF YIELD GAP
```{r}

#yg_yield_tt-tests
yg_yield_ttests_1 <- list()
yg_yield_ttests_2.5 <- list()
yg_yield_ttests_5 <- list()

#table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")
keep <- c("Banana Beer", "Banana Food", "Beans", "Cassava", "Field Peas", "Groundnut", "Irish Potatoes", "Maize", "Paddy", "Pyrethrum", "Sorghum", "Soyabeans", "Sweet Potatoes", "Wheat")

#t-test of yield ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_yield_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(kg_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_yield_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(kg_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_yield_ttests_5[[i]] <- stat5
}

#yg_yield_tt-tests
yg_yield_ttests_1 
yg_yield_ttests_2.5 
yg_yield_ttests_5 

#Table
yg_yield_table <- map_df(yg_yield_ttests_5, tidy)
names(yg_yield_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")

# dataframe including differences
yg_yield_table2 <- as.data.frame(yg_yield_table)
yg_yield_table2 <- select(yg_yield_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
yg_yield_table2 <- mutate(yg_yield_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
rownames(yg_yield_table2) <-  c("Banana Beer", "Banana Food", "Beans", "Cassava", "Field Peas", "Groundnut", "Irish Potatoes", "Maize", "Paddy", "Pyrethrum", "Sorghum", "Soyabeans", "Sweet Potatoes", "Wheat")
View(yg_yield_table2)

#Summarize number of entries per crop

```



####PESTICIDES AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_pest_ttests_1 <- list()
yg_pest_ttests_2.5 <- list()
yg_pest_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")
keep <- c("Beans", "Irish Potatoes", "Maize", "Paddy")

#t-test of pesticide ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(pest_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_pest_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(pest_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_pest_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(pest_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_pest_ttests_5[[i]] <- stat5
}

#yg_pest_tt-tests
yg_pest_ttests_1 
yg_pest_ttests_2.5 
yg_pest_ttests_5 

# Table if top/bottom 5% eliminated
yg_pest_table <- map_df(yg_pest_ttests_2.5, tidy)
# names(yg_pest_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")
# 
# dataframe including differences
# yg_pest_table2 <- as.data.frame(yg_pest_table)
# yg_pest_table2 <- select(yg_pest_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
# yg_pest_table2 <- mutate(yg_pest_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
# rownames(yg_pest_table2) <- c("Beans", "Irish Potatoes", "Maize", "Paddy")
# View(yg_pest_table2)

```


####INORGANIC FERTILIZER AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_inorg_ttests_1 <- list()
yg_inorg_ttests_2.5 <- list()
yg_inorg_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_45, useNA="always")
keep <- c("Beans", "Irish Potatoes", "Maize", "Wheat")

#t-test of inorganic fertilizer ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_inorg_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_inorg_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_inorg_ttests_5[[i]] <- stat5
}

#yg_inorg_tt-tests
yg_inorg_ttests_1 
yg_inorg_ttests_2.5 
yg_inorg_ttests_5 

# #Table
# yg_inorg_table <- map_df(yg_inorg_ttests_5, tidy)
# names(yg_inorg_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")
# 
# yg_inorg_table2 <- as.data.frame(yg_inorg_table)
# yg_inorg_table2 <- select(yg_inorg_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
# yg_inorg_table2 <- mutate(yg_inorg_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
# rownames(yg_inorg_table2) <-  c("Beans", "Irish Potatoes", "Maize", "Wheat")
# View(yg_inorg_table2)

```


####ORGANIC FERTILIZER AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_org_ttests_1 <- list()
yg_org_ttests_2.5 <- list()
yg_org_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_39, useNA="always")
keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")

#t-test of organic fertilizer ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(org_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_org_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(org_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_org_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(org_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_org_ttests_5[[i]] <- stat5
}

#yg_org_tt-tests
yg_org_ttests_1 
yg_org_ttests_2.5 
yg_org_ttests_5 


# #Table
# yg_org_table <- map_df(yg_org_ttests_5, tidy)
# names(yg_org_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")
# 
# yg_org_table2 <- as.data.frame(yg_org_table)
# yg_org_table2 <- select(yg_org_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
# yg_org_table2 <- mutate(yg_org_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
# rownames(yg_org_table2) <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")
# View(yg_org_table2)


```



####HISTOGRAMS AND DENSITY PLOTS OF YIELD (KG/HA)
```{r for() loop historgrams}

cr <- as.character(unique(jdf_n30_2.5$crop_name))
hist_crop_yield_2.5 <- list()
hist_crop_yield_5 <- list()

#for() loop histograms of crop yield
for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_2.5[jdf_n30_2.5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_histogram(bins = 20, color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Histogram of", cr[i], "Yield", sep=" "))
  hist_crop_yield_2.5[[i]] <- plot 
}
hist_crop_yield_2.5

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_5[jdf_n30_5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_histogram(bins = 20, color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Histogram of", cr[i], "Yield", sep=" "))
  hist_crop_yield_5[[i]] <- plot 
}
#hist_crop_yield_5

# --------------------------------------------

#for() loop density plot of crop yield

cr <- as.character(unique(jdf_n30_2.5$crop_name))
dens_crop_yield_2.5 <- list()
dens_crop_yield_5 <- list()

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_2.5[jdf_n30_2.5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_density(kernel = "gaussian", color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Density Plot of", cr[i], "Yield", sep=" "))+
    scale_fill_manual()
  dens_crop_yield_2.5[[i]] <- plot 
}
dens_crop_yield_2.5

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_5[jdf_n30_5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_density(kernel = "gaussian", color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Density Plot of", cr[i], "Yield", sep=" "))+
    scale_fill_manual()
  dens_crop_yield_5[[i]] <- plot 
}
#dens_crop_yield_5




```

####Commonly Used Indicators
*Intercrop - ag4a_04 (1 yes/2 no)
*Erosion control - ag3a_14 (1 yes/2 no) ag3a_15_1, ag3a_15_2, (type, primary, secondary)
*Area harvested - ag4a_08
*Inorganic fertilizer  - ag3a_45 (1 yes/2 no), ag3a_47 (kg)
*Organic fertilizer  - ag3a_39 (1 yes/2 no), ag3a_40 (kg)
*Pesticide/herbicide - ag3a_58 (1 yes/2 no), ag3a_59 {1: 'Pesticide', 2: 'Herbicide', 3: 'Fungicide'}, ag3a_60_1 (kg), pesticide_kg, herbicide_kg, fungicide_kg


####Yield Gap ~ Erosion Control
```{r}

#Yield Gap ~ Erosion Control
ggplot(data = filter(jdf_n30_2.5, ag3a_14 != "NA"), aes(yield_gap, fill=ordered(ag3a_14, levels=c("Yes", "No")))) +
  geom_bar(stat="count", position = "fill")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
  xlab("Lower/ Higher Yield")+
  ylab("Erosion Control")+
  ggtitle("Erosion Control as a Function of Yield Gap")+
  scale_fill_discrete(name="Erosion Control", labels =c("Yes", "No"))

```


```

