---
title: "VSR Final Graph Style"
author: "Rachel Kenny"
date: "3/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
This describes the code used to make graphs consistent. theme_VSR should be applied to all graphs, x and y axis should be scaled when appropriate, Zissou1 colors should be applied.  Finally, save the graph as a high quality png and check for appropriate scaling of elements.


####theme_VSR()
Will apply theme_classic plus updated font (Palatino), bold title (left justified and slightly shifted with hjust), and bold legend title  
  
  
```{r, messages = FALSE}
theme_VSR <- function () { 
    theme_classic(base_size=10, base_family="Palatino")+
    theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title = element_text(face="bold"))
}

```

**Scale axes**  
*Note that the values for expansion of the axis will have to adjust, but should adjust such that there is a small amount of space on the left side*  
```{r, eval = FALSE}
+scale_x_discrete(expand = c(0.015, 0))  
+scale_x_continuous(expand = c(0.015, 0))  
+scale_y_discrete(expand = c(0, 0))  
+scale_y_continuous(expand = c(0, 0)) 
```
  
  
####Wes Anderson Zissou1 Color Palette:
- **Red:** "#e03c21"  
- **Dark yellow:** "#dab03a"  
- **Light yellow:** "#e6cd4f"  
- **Light blue:** "#85b6c4"  
- **Dark blue:** "#5498af"  
  
  
####Expanded color palette (11 colors)
- **Red:** "#e03c21"  
- **Light red:** "#de6e5b"  
- **Orange:** "eb8932"  
- **Dark yellow:** "#dab03a"  
- **Light yellow:** "#e6cd4f"  
- **Light green-yellow:** "#b4ce8f"  
- **Light green-blue:** "90c3ab"  
- **Dark green-blue:** "449d8b"  
- **Dark green:** "#5498af"  
- **Light blue:** "#85b6c4"  
- **Dark blue:** "#5498af"  
  
  
  
####Uses for palette
```{r, eval=FALSE}
#palette
wes_palette("Zissou1")  

#Use of Zissou palette  
+scale_fill_manual(values = wes_palette("Zissou1")) 
                   
#Use of reversed Zissou palette 
+scale_fill_manual(values = rev(wes_palette("Zissou1")) 

#Two colors to indicate treatments
+scale_fill_manual(values = c("#e6cd4f", "#85b6c4")) 

#Continuous palett
pal <- wes_palette("Zissou1", 21, type = "continuous")
scale_fill_gradientn(colours = pal)

#If distinct colors are needed
+scale_fill_manual(values = c("#e03c21", "#de6e5b", "eb8932", "#dab03a", "#e6cd4f", "#b4ce8f", "90c3ab", "449d8b", "#5498af", "#85b6c4", "#5498af") 
                   
+scale_color_manual(values = c("#a6cd5b", "#f59082", "#72bad3", "#752559", "#f5d05d", "#eb4024", "#2c6b96", "#eb8932", "#7789cc"))                   
```



####To save pngs, use this code and modify as needed

```{r, eval=FALSE}
#Small graph  
ggsave("plot_name.png", plot = plot_name, device = "png", path = "~/Documents/",
  width = 4, height = 3, units = c("in"),
  dpi = 300)

#Halfpage graph 
ggsave("plot_name.png", plot = plot_name, device = "png", path = "~/Documents/",
  width = 7.5, height = 4, units = c("in"),
  dpi = 300)
```


#Example
```{r}



```



