---
title: "Vital Signs Rwanda Yield Gap Analysis"
author: "Rachel Kenny"
date: "1/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


####Commonly Used Indicators
  # *Intercrop - ag4a_04 (1 yes/2 no)
  # *Erosion control - ag3a_14 (1 yes/2 no) ag3a_15_1, ag3a_15_2, (type: primary, secondary)
  # *Area harvested - ag4a_08
  # *Inorganic fertilizer  - ag3a_45 (1 yes/2 no), ag3a_47 (kg)
  # *Organic fertilizer  - ag3a_39 (1 yes/2 no), ag3a_40 (kg)
  # *Pesticide/herbicide - ag3a_58 (1 yes/2 no), ag3a_59 {1: 'Pesticide', 2: 'Herbicide', 3:  'Fungicide'}, ag3a_60_1 (kg), pesticide_kg, herbicide_kg, fungicide_kg

#### Load libraries and data
```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(broom)
library(purrr)

fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season_fieldcrop.csv"))
hh_fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_fieldcrop.csv"))
field_season <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season.csv"))

#View(household_field_season_fieldcrop)

#Filter fieldcrop, treat factors as factors and numeric as numeric
fieldcrop <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15 != "na")
fieldcrop <- filter(fieldcrop, ag4a_15_unit == "Kg")
fieldcrop$crop_name <- as.factor(fieldcrop$crop_name)
fieldcrop$crop_name[which(fieldcrop$crop_name=="Irish potatoes")] <- "Irish Potatoes"
fieldcrop$crop_name[which(fieldcrop$crop_name=="Blood fruit")] <- "Blood Fruit"  
fieldcrop$ag4a_15_unit[which(fieldcrop$ag4a_15_unit=="Liter")] <- "Kg"
fieldcrop$ag4a_15 <- as.numeric(fieldcrop$ag4a_15)
fieldcrop$ag4a_15_unit <- as.factor(fieldcrop$ag4a_15_unit)
fieldcrop$ag4a_08 <- as.numeric(fieldcrop$ag4a_08)

#Filter field_season, treat factors as factors and numeric as numeric
field_season <- filter(field_season, country == 'RWA',  ag3a_03 == 'Cultivated' )
field_season$ag3a_39 <- as.factor(field_season$ag3a_39)
field_season$ag3a_39a <- as.factor(field_season$ag3a_39a)
field_season$ag3a_39a_other <- as.factor(field_season$ag3a_39a_other)
field_season$ag3a_40 <- as.numeric(field_season$ag3a_40)
field_season$ag3a_45 <- as.factor(field_season$ag3a_45)
field_season$ag3a_47 <- as.factor(field_season$ag3a_47)
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Irish potatoes")] <- "Irish Potatoes"
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Blood fruit")] <- "Blood Fruit"

#factors for hh fieldcrop
hh_fieldcrop$landscape_no <- as.factor(hh_fieldcrop$landscape_no)

```

####Create Joined Dataset
```{r}

#Join
joined_df <- inner_join(field_season, fieldcrop, by =c("id"= "parent_id", 'round', "landscape_no", "country", "field_no", "hh_refno", "season", "latitude", "longitude"))

#Add column for 
joined_df <- mutate(joined_df, kg_peracre = ag4a_15/ag4a_08)
joined_df <- mutate(joined_df, kg_perha = kg_peracre/.404686)

#per acre planted 
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/4")] <- .25
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/2")] <- .5
joined_df$ag4a_02[which(joined_df$ag4a_02=="3/4")] <- .75
joined_df$ag4a_02[which(joined_df$ag4a_02=="Almost All")] <- 1
joined_df$ag4a_02 <- as.numeric(joined_df$ag4a_02)
joined_df <- mutate(joined_df, kg_peracre_planted = case_when(ag4a_01 == TRUE ~ kg_peracre, ag4a_01 == FALSE ~ ag4a_15/(ag4a_08*ag4a_02)))
joined_df <-mutate(joined_df, kg_perha_planted = kg_peracre_planted/.404686)

#value per hectare planted 
joined_df <- filter(joined_df, kg_perha_planted != Inf )
joined_df <- mutate(joined_df, value_peracre = ag4a_16/ag4a_08)  
joined_df <- mutate(joined_df, value_peracre_planted = case_when(ag4a_01 == TRUE ~ value_peracre, ag4a_01 == FALSE ~ value_peracre*ag4a_02))
joined_df <-mutate(joined_df, value_perha_planted = value_peracre/.404686)

#pesticides
joined_df <- mutate(joined_df, pesticide_use_kg = ifelse(ag3a_60_2 == "Millilitre", ag3a_60_1*0.001, ag3a_60_1))
joined_df$round <- as.factor(joined_df$round)
joined_df <- mutate(joined_df, pesticide_kg = ifelse(ag3a_59 == "Pesticide", ag3a_60_1, NA))
joined_df <- mutate(joined_df, herbicide_kg = ifelse(ag3a_59 == "Herbicide", ag3a_60_1, NA))
joined_df <- mutate(joined_df, fungicide_kg = ifelse(ag3a_59 == "Fungicide", ag3a_60_1, NA))

#Add column for pesticide kg per hectare planted
joined_df <- mutate(joined_df, pest_peracre = ag3a_60_1/ag4a_08)
joined_df <- mutate(joined_df, pest_perha = pest_peracre*.404686)
joined_df <- mutate(joined_df, pest_peracre_planted = case_when(ag4a_01 == TRUE ~ pest_peracre,
                                                              ag4a_01 == FALSE ~ ag3a_60_1/ag4a_08*ag4a_02))
joined_df <-mutate(joined_df, pest_perha_planted = pest_peracre_planted *.404686)
#joined_df <- filter(joined_df, pest_perha != Inf )

#Add column for inorg fert kg per hectare planted
joined_df$ag3a_47 <- as.numeric(joined_df$ag3a_47)
joined_df <- mutate(joined_df, inorg_peracre = ag3a_47/ag4a_08)
joined_df <- mutate(joined_df, inorg_perha = inorg_peracre*.404686)
joined_df <- mutate(joined_df, inorg_peracre_planted = case_when(ag4a_01 == TRUE ~ inorg_peracre, ag4a_01 == FALSE ~ ag3a_47/ag4a_08*ag4a_02))
joined_df <-mutate(joined_df, inorg_perha_planted = inorg_peracre_planted *.404686)
#joined_df <- filter(joined_df, inorg_perha != Inf )

#Add column for org fert kg per hectare planted
joined_df$ag3a_40 <- as.numeric(joined_df$ag3a_40)
joined_df <- mutate(joined_df, org_peracre = ag3a_40/ag4a_08)
joined_df <- mutate(joined_df, org_perha = org_peracre*.404686)
joined_df <- mutate(joined_df, org_peracre_planted = case_when(ag4a_01 == TRUE ~ org_peracre,
                                                              ag4a_01 == FALSE ~ ag3a_40/ag4a_08*ag4a_02))
joined_df <-mutate(joined_df, org_perha_planted = org_peracre_planted *.404686)
#joined_df <- filter(joined_df, org_perha != Inf )

#Summarize number of entries per crop
joined_df %>%
  group_by(crop_name) %>%
  tally()

table(joined_df$crop_name, joined_df$ag4a_04, useNA="always")

#austins code to look at later leels
#check <- filter(round_1, ag4a_04 == TRUE) %>% droplevels()
#check2 <- filter(round_2, ag4a_04 == TRUE) %>%  droplevels()

#subset data n>30, reveals top 10 plots
jdf_n30 <- filter(joined_df, crop_name == "Banana Beer" | crop_name == "Banana Food" | crop_name == "Beans" | crop_name == "Cassava" | crop_name == "Field Peas" | crop_name == "Groundnut" | crop_name == "Irish Potatoes" | crop_name == "Maize" | crop_name == "Paddy" | crop_name == "Pyrethrum" | crop_name == "Sorghum" | crop_name == "Soyabeans" | crop_name == "Sweet Potatoes" | crop_name == "Wheat")

```


```{r}

joined_df %>%
  group_by(crop_name) %>%
  tally()

joined_df %>%
  group_by(landscape_no) %>%
  summarize(mean_value_perha = mean(value_perha_planted, na.rm = TRUE))

land_no <- as.character(unique(joined_df$landscape_no))
crop_count <- list()

for(i in 1:length(land_no)){
  table_new <- joined_df %>%
  filter(landscape_no == land_no[i]) %>% 
  group_by(crop_name) %>%
  tally()
  crop_count[[i]] <- table_new 
}
crop_count

#count = tally(crop_name), 

land_no <- as.character(unique(joined_df$landscape_no))
table_list <- list()

for(i in 1:length(land_no)){
  table_new <- joined_df %>%
  filter(landscape_no == land_no[i]) %>% 
  group_by(crop_name) %>%
  summarize(mean_value_perha = mean(value_perha_planted, na.rm = TRUE))
  table_list[[i]] <- table_new 
}
table_list

```























```{r}

cr <- unique(jdf_n30$crop_name)

jdf_n30 <- jdf_n30[!is.na(jdf_n30$ag4a_04),] #Removes NA value for intercropping

#create exclude variable
jdf_n30$exclude_1 <- NA
jdf_n30$exclude_2.5 <- NA
jdf_n30$exclude_5 <- NA

for(i in 1:length(cr)){
jdf_n30$exclude_1[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.99) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.01), 1, 0)

jdf_n30$exclude_2.5[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.975) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.025), 1, 0)
    
jdf_n30$exclude_5[jdf_n30$crop_name==cr[i]] <- ifelse(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] > quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.95) | jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]] < quantile(jdf_n30$kg_perha_planted[jdf_n30$crop_name==cr[i]], probs=0.05), 1, 0)
}

table(jdf_n30$exclude_1, useNA="always")
table(jdf_n30$exclude_2.5, useNA="always")
table(jdf_n30$exclude_5, useNA="always")

jdf_n30_1 <- jdf_n30[jdf_n30$exclude_1==0,]
jdf_n30_2.5 <- jdf_n30[jdf_n30$exclude_2.5==0,]
jdf_n30_5 <- jdf_n30[jdf_n30$exclude_5==0,]

#create yield gap variable 
dta <- list(jdf_n30_1, jdf_n30_2.5, jdf_n30_5)
for(i in 1:length(dta)){
  for(j in 1:length(cr)){
    dta[[i]]$yield_gap[dta[[i]]$crop_name==cr[j]] <- ifelse(dta[[i]]$kg_perha_planted[dta[[i]]$crop_name==cr[j]] > quantile(dta[[i]]$kg_perha_planted[dta[[i]]$crop_name==cr[j]], probs=0.75), 1, 0)
  }
}
#table(dta[[1]]$yield_gap, useNA="always") #code to check number of entries
```

####T-tests
Yield ~ Intercrop
```{r}
#yield_intercrop_tt-tests
yield_intercrop_ttests_1 <- list()
yield_intercrop_ttests_2.5 <- list()
yield_intercrop_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag4a_04, useNA="always")


keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans",  "Banana Food", "Field Peas", "Groundnut", "Sweet Potatoes")

#t-test of yield ~ intercrop (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df,
               alternative="greater")
  yield_intercrop_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df1,
               alternative="greater")
  yield_intercrop_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag4a_04,
               data=df2,
               alternative="greater")
  yield_intercrop_ttests_5[[i]] <- stat5
}

#yield_intercrop_tt-tests
yield_intercrop_ttests_1 
yield_intercrop_ttests_2.5 
yield_intercrop_ttests_5 

yield_intercrop_table <- map_df(yield_intercrop_ttests_5, tidy)
names(yield_intercrop_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
yield_intercrop_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]

```

####T-tests Yield
Yield ~ Pesticide
```{r}
#yield_pesticide_tt-tests
yield_pesticide_ttests_1 <- list()
yield_pesticide_ttests_2.5 <- list()
yield_pesticide_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")


keep <- c("Beans", "Irish Potatoes", "Maize", "Paddy")

#t-test of yield ~ pesticide (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df,
               alternative="greater")
  yield_pesticide_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df1,
               alternative="greater")
  yield_pesticide_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_58,
               data=df2,
               alternative="greater")
  yield_pesticide_ttests_5[[i]] <- stat5
}

#yield_pesticide_tt-tests
yield_pesticide_ttests_1 
yield_pesticide_ttests_2.5 
yield_pesticide_ttests_5 

yield_pesticide_table <- map_df(yield_pesticide_ttests_5, tidy)
names(yield_pesticide_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
yield_pesticide_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```


Yield ~ Organic Fertilizer
```{r}
#yield_org_tt-tests
yield_org_ttests_1 <- list()
yield_org_ttests_2.5 <- list()
yield_org_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_39, useNA="always")


keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")

#t-test of yield ~ organic fertilizer (yes/no) 
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df,
               alternative="greater")
  yield_org_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df1,
               alternative="greater")
  yield_org_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_39,
               data=df2,
               alternative="greater")
  yield_org_ttests_5[[i]] <- stat5
}

#yield_org_tt-tests
yield_org_ttests_1 
yield_org_ttests_2.5 
yield_org_ttests_5 

yield_org_table <- map_df(yield_org_ttests_2.5, tidy)
names(yield_org_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
yield_org_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```

Yield ~ Inorganic Fertilizer
```{r}
#yield_inorg_tt-tests
yield_inorg_ttests_1 <- list()
yield_inorg_ttests_2.5 <- list()
yield_inorg_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_45, useNA="always")
table(joined_df$crop_name, joined_df$ag3a_45, useNA="always")

keep <- c("Beans", "Irish Potatoes", "Maize", "Wheat")

#t-test of yield ~ inorg (yes/no) dta is list, take first object, only retain rows where crop name = i
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df,
               alternative="greater")
  yield_inorg_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
    stat2.5 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df1,
               alternative="greater")
  yield_inorg_ttests_2.5[[i]] <- stat2.5

    df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
    stat5 <- t.test(kg_perha_planted ~ ag3a_45,
               data=df2,
               alternative="greater")
  yield_inorg_ttests_5[[i]] <- stat5
}

#yield_inorg_tt-tests
yield_inorg_ttests_1 
yield_inorg_ttests_2.5 
yield_inorg_ttests_5 

yield_inorg_table <- map_df(yield_inorg_ttests_2.5, tidy)
names(yield_inorg_table) <- c("estimate", "Mean 1", "Mean 2", "t-statistic", "p-value", "df")
yield_inorg_table[c("Mean 1", "Mean 2", "t-statistic", "p-value")]


```



####YIELD AS A FUNCTION OF YIELD GAP
```{r}

#yg_yield_tt-tests
yg_yield_ttests_1 <- list()
yg_yield_ttests_2.5 <- list()
yg_yield_ttests_5 <- list()

#table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")
keep <- c("Banana Beer", "Banana Food", "Beans", "Cassava", "Field Peas", "Groundnut", "Irish Potatoes", "Maize", "Paddy", "Pyrethrum", "Sorghum", "Soyabeans", "Sweet Potatoes", "Wheat")

#t-test of yield ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(kg_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_yield_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(kg_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_yield_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(kg_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_yield_ttests_5[[i]] <- stat5
}

#yg_yield_tt-tests
yg_yield_ttests_1 
yg_yield_ttests_2.5 
yg_yield_ttests_5 

#Table
yg_yield_table <- map_df(yg_yield_ttests_5, tidy)
names(yg_yield_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")

#dataframe including differences
yg_yield_table2 <- as.data.frame(yg_yield_table)
yg_yield_table2 <- select(yg_yield_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
yg_yield_table2 <- mutate(yg_yield_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
rownames(yg_yield_table2) <-  c("Banana Beer", "Banana Food", "Beans", "Cassava", "Field Peas", "Groundnut", "Irish Potatoes", "Maize", "Paddy", "Pyrethrum", "Sorghum", "Soyabeans", "Sweet Potatoes", "Wheat")
View(yg_yield_table2)

```



####PESTICIDES AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_pest_ttests_1 <- list()
yg_pest_ttests_2.5 <- list()
yg_pest_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_58, useNA="always")
keep <- c("Beans", "Irish Potatoes", "Maize", "Paddy")

#t-test of pesticide ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(pest_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_pest_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(pest_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_pest_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(pest_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_pest_ttests_5[[i]] <- stat5
}

#yg_pest_tt-tests
yg_pest_ttests_1 
yg_pest_ttests_2.5 
yg_pest_ttests_5 

#Table if top/bottom 5% eliminated
yg_pest_table <- map_df(yg_pest_ttests_5, tidy)
names(yg_pest_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")

#dataframe including differences
yg_pest_table2 <- as.data.frame(yg_pest_table)
yg_pest_table2 <- select(yg_pest_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
yg_pest_table2 <- mutate(yg_pest_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
rownames(yg_pest_table2) <- c("Beans", "Irish Potatoes", "Maize", "Paddy")
View(yg_pest_table2)

```


####INORGANIC FERTILIZER AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_inorg_ttests_1 <- list()
yg_inorg_ttests_2.5 <- list()
yg_inorg_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_45, useNA="always")
keep <- c("Beans", "Irish Potatoes", "Maize", "Wheat")

#t-test of inorganic fertilizer ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_inorg_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_inorg_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(inorg_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_inorg_ttests_5[[i]] <- stat5
}

#yg_inorg_tt-tests
yg_inorg_ttests_1 
yg_inorg_ttests_2.5 
yg_inorg_ttests_5 

#Table
yg_inorg_table <- map_df(yg_inorg_ttests_5, tidy)
names(yg_inorg_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")

yg_inorg_table2 <- as.data.frame(yg_inorg_table)
yg_inorg_table2 <- select(yg_inorg_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
yg_inorg_table2 <- mutate(yg_inorg_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
rownames(yg_inorg_table2) <-  c("Beans", "Irish Potatoes", "Maize", "Wheat")
View(yg_inorg_table2)

```


####ORGANIC FERTILIZER AS A FUNCTION OF YIELD GAP
```{r}

#yg_pest_tt-tests
yg_org_ttests_1 <- list()
yg_org_ttests_2.5 <- list()
yg_org_ttests_5 <- list()

table(jdf_n30$crop_name, jdf_n30$ag3a_39, useNA="always")
keep <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")

#t-test of organic fertilizer ~ yield gap
for(i in 1:length(keep)){
  df <- dta[[1]][dta[[1]]$crop_name==keep[i],]
  stat1 <- t.test(org_perha_planted ~ yield_gap,
               data=df,
               alternative="less")
  yg_org_ttests_1[[i]] <- stat1
  
  df1 <- dta[[2]][dta[[2]]$crop_name==keep[i],]
  stat2.5 <- t.test(org_perha_planted ~ yield_gap,
               data=df1,
               alternative="less")
  yg_org_ttests_2.5[[i]] <- stat2.5

  df2 <- dta[[3]][dta[[3]]$crop_name==keep[i],]
  stat5 <- t.test(org_perha_planted ~ yield_gap,
               data=df2,
               alternative="less")
  yg_org_ttests_5[[i]] <- stat5
}

#yg_org_tt-tests
yg_org_ttests_1 
yg_org_ttests_2.5 
yg_org_ttests_5 


#Table
yg_org_table <- map_df(yg_org_ttests_5, tidy)
names(yg_org_table) <- c("estimate", "Mean_1", "Mean_2", "t-statistic", "p-value", "df", "CI", "Inf?", "test", "alternative")

yg_org_table2 <- as.data.frame(yg_org_table)
yg_org_table2 <- select(yg_org_table2, "Mean_1", "Mean_2", "t-statistic", "p-value")
yg_org_table2 <- mutate(yg_org_table2, difference = ((Mean_2 - Mean_1) * (100/Mean_1)))
rownames(yg_org_table2) <- c("Banana Beer", "Beans", "Cassava", "Irish Potatoes", "Maize", "Sorghum", "Soyabeans", "Sweet Potatoes")
View(yg_org_table2)



```




####HISTOGRAMS AND DENSITY PLOTS OF YIELD (KG/HA)
```{r for() loop historgrams}

cr <- as.character(unique(jdf_n30_2.5$crop_name))
hist_crop_yield_2.5 <- list()
hist_crop_yield_5 <- list()

#for() loop histograms of crop yield
for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_2.5[jdf_n30_2.5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_histogram(bins = 20, color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Histogram of", cr[i], "Yield", sep=" "))
  hist_crop_yield_2.5[[i]] <- plot 
}
hist_crop_yield_2.5

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_5[jdf_n30_5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_histogram(bins = 20, color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Histogram of", cr[i], "Yield", sep=" "))
  hist_crop_yield_5[[i]] <- plot 
}
#hist_crop_yield_5

# --------------------------------------------

#for() loop density plot of crop yield

cr <- as.character(unique(jdf_n30_2.5$crop_name))
dens_crop_yield_2.5 <- list()
dens_crop_yield_5 <- list()

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_2.5[jdf_n30_2.5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_density(kernel = "gaussian", color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Density Plot of", cr[i], "Yield", sep=" "))+
    scale_fill_manual()
  dens_crop_yield_2.5[[i]] <- plot 
}
dens_crop_yield_2.5

for(i in 1:length(cr)){
  plot <- ggplot(jdf_n30_5[jdf_n30_5$crop_name==cr[i],], aes(kg_perha_planted)) + 
    geom_density(kernel = "gaussian", color="darkblue", fill="lightblue") +
    xlab("Yield (kg/hectare planted)")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
    ggtitle(paste("Density Plot of", cr[i], "Yield", sep=" "))+
    scale_fill_manual()
  dens_crop_yield_5[[i]] <- plot 
}
#dens_crop_yield_5




```

####Commonly Used Indicators
*Intercrop - ag4a_04 (1 yes/2 no)
*Erosion control - ag3a_14 (1 yes/2 no) ag3a_15_1, ag3a_15_2, (type, primary, secondary)
*Area harvested - ag4a_08
*Inorganic fertilizer  - ag3a_45 (1 yes/2 no), ag3a_47 (kg)
*Organic fertilizer  - ag3a_39 (1 yes/2 no), ag3a_40 (kg)
*Pesticide/herbicide - ag3a_58 (1 yes/2 no), ag3a_59 {1: 'Pesticide', 2: 'Herbicide', 3: 'Fungicide'}, ag3a_60_1 (kg), pesticide_kg, herbicide_kg, fungicide_kg


