---
title: "Vital Signs Rwanda - Descriptives Master Sheet"
author: "Rachel Kenny and Meghan Cook"
date: "1/14/2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Tables of Contents
1. Data Wrangling
2. Descriptives
  a. Pesticide
  b. Organic Fertilizer
  c. Inorganic Fertilizer
  d. Quantity of Crop Harvest
  e. Reason for Intercropping
  f. Soil Quality
  g. Crop Residue Use
  h. Food Loss

---

##Data Wrangling

```{r}

#load libraries
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(broom)
library(purrr)
library(readr)
library(RColorBrewer)
library(coefplot)
library(wesanderson)

#load data
fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season_fieldcrop.csv"))
hh_fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_fieldcrop.csv"))
field_season <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season.csv"))
hh_indiv <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_individual.csv"))

#View(household_field_season_fieldcrop)
```


```{r}
#Filter fieldcrop, treat factors as factors and numeric as numeric
fieldcrop <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15 != "na")
fieldcrop$ag4a_08 <- as.numeric(fieldcrop$ag4a_08)
fieldcrop$ag4a_15 <- as.numeric(fieldcrop$ag4a_15)
fieldcrop$ag4a_15_unit <- as.factor(fieldcrop$ag4a_15_unit)
fieldcrop$crop_name <- as.factor(fieldcrop$crop_name)
fieldcrop$ag4a_15_unit[which(fieldcrop$ag4a_15_unit=="Liter")] <- "Kg" #because this is a misentry
fieldcrop <- filter(fieldcrop, ag4a_15_unit == "Kg")

#fix crop name mismatches
fieldcrop$crop_name[which(fieldcrop$crop_name=="Irish potatoes")] <- "Irish Potatoes"
fieldcrop$crop_name[which(fieldcrop$crop_name=="Blood fruit")] <- "Blood Fruit"  
hh_fieldcrop$ag5a_21[which(hh_fieldcrop$ag5a_21=="Mammals (Rodent)")] <- "Rodents"

#Filter field_season, treat factors as factors and numeric as numeric
field_season <- filter(field_season, country == 'RWA',  ag3a_03 == 'Cultivated' )
field_season$ag3a_39 <- as.factor(field_season$ag3a_39)
field_season$ag3a_39a <- as.factor(field_season$ag3a_39a)
field_season$ag3a_39a_other <- as.factor(field_season$ag3a_39a_other)
field_season$ag3a_40 <- as.numeric(field_season$ag3a_40)
field_season$ag3a_45 <- as.factor(field_season$ag3a_45)
field_season$ag3a_47 <- as.factor(field_season$ag3a_47)

#fix crop name mismatch
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Irish potatoes")] <- "Irish Potatoes"
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Blood fruit")] <- "Blood Fruit"

#fset landscape # as factor in household survey data
hh_fieldcrop$landscape_no <- as.factor(hh_fieldcrop$landscape_no)

#Join fieldcrop and field_season dataframes
joined_df <- inner_join(field_season, fieldcrop, by =c("id"= "parent_id", 'round', "landscape_no", "country", "field_no", "hh_refno", "season"))

#Add columns for yield
joined_df <- mutate(joined_df, kg_peracre = ag4a_15/ag4a_08)
joined_df <- mutate(joined_df, kg_perha = kg_peracre*(1/.404686))

#per acre planted 
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/4")] <- .25
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/2")] <- .5
joined_df$ag4a_02[which(joined_df$ag4a_02=="3/4")] <- .75
joined_df$ag4a_02[which(joined_df$ag4a_02=="Almost All")] <- 1
joined_df$ag3a_40 <- as.numeric(joined_df$ag3a_40)
joined_df$ag3a_47 <- as.numeric(joined_df$ag3a_47)
joined_df$ag4a_02 <- as.numeric(joined_df$ag4a_02)
joined_df$round <- as.factor(joined_df$round)

joined_df <- mutate(joined_df, kg_peracre_planted = case_when(ag4a_01 == TRUE ~ kg_peracre, ag4a_01 == FALSE ~ ag4a_15/(ag4a_08*ag4a_02))) %>% 
  mutate(kg_perha_planted = kg_peracre_planted *(1/.404686))

#value per hectare planted 
joined_df <- filter(joined_df, kg_perha_planted != Inf) %>% 
  mutate(value_peracre = ag4a_16/ag4a_08) %>% 
  mutate(value_perha = value_peracre*(1/.404686)) %>% 
  mutate(value_peracre_planted = case_when(ag4a_01 == TRUE ~ value_peracre, ag4a_01 == FALSE ~ ag4a_16/ag4a_08*ag4a_02)) %>% 
  mutate(value_perha_planted = value_peracre_planted *(1/.404686))


#Add column for pesticide kg per hectare planted
joined_df <-mutate(joined_df, pesticide_use_kg = ifelse(ag3a_60_2 == "Millilitre", ag3a_60_1*0.001, ag3a_60_1)) %>% 
  mutate(pesticide_use_kg = case_when(ag3a_58 == TRUE ~ pesticide_use_kg, ag3a_58 == FALSE ~ 0)) %>% 
  mutate(pest_peracre = pesticide_use_kg/ag4a_08) %>% 
  mutate(pest_perha = pest_peracre*(1/.404686)) %>% 
  mutate(pest_peracre_planted = case_when(ag4a_01 == TRUE ~ pest_peracre, ag4a_01 == FALSE ~ pest_peracre/ag4a_02)) %>% 
  mutate(pest_perha_planted = pest_peracre_planted *(1/.404686))

#Add column for inorg fert kg per hectare planted
joined_df <- mutate(joined_df, inorg_peracre = ag3a_47/ag4a_08) %>% 
  mutate(inorg_perha = inorg_peracre*(1/.404686)) %>%  
  mutate(inorg_perha_planted = case_when(ag4a_01 == TRUE ~ inorg_perha, ag4a_01 == FALSE ~ inorg_perha/ag4a_02)) %>% 
  mutate(inorg_perha_planted = case_when(ag3a_45 ==TRUE ~ inorg_perha_planted, ag3a_45 == FALSE ~ 0 ))

#Add column for org fert kg per hectare planted
joined_df <- mutate(joined_df, org_peracre = ag3a_40/ag4a_08) %>% 
  mutate(org_perha = org_peracre*(1/.404686)) %>%
  mutate(org_perha_planted = case_when(ag4a_01 == TRUE ~ org_peracre, ag4a_01 == FALSE ~ org_perha/ag4a_02)) %>% 
  mutate(org_perha_planted = case_when(ag3a_39 ==TRUE ~ org_perha_planted, ag3a_39 == FALSE ~ 0 ))

# Create df for each round
round_1 <- filter(joined_df, round == "1")
round_2 <- filter(joined_df, round == "2")

# Rename landscape levels
# joined_df_L <- joined_df
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L01")] <- "1"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L02")] <- "2"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L03")] <- "3"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L04")] <- "4"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L06")] <- "6"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L07")] <- "7"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L08")] <- "8"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L10")] <- "10"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L11")] <- "11"
# joined_df_L$landscape_no[which(joined_df_L$landscape_no=="L12")] <- "12"


#View(joined_df)
#levels(joined_df$landscape_no)

```

---

###Set style
```{r}

theme_vsr <- function () { 
    theme_classic(base_size=9, base_family="Helvetica")+
    theme(plot.title = element_text(face="bold"), legend.title = element_text(face="bold"))
}

```


##2. Descriptives

###Crops grown across landscape
```{r}

A_crops_grown <- ggplot(filter(joined_df, crop_name != "NA"), aes(x= crop_name, fill=factor(landscape_no)))+
 geom_bar(stat = "count", position = 'stack')+
  theme_vsr()+
 theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3), plot.title = element_text(hjust = 0.5))+
 xlab ("Crop Type")+
 ylab("Number of Fields")+
 ggtitle("Number of Fields Growing Each Crop Type per Landscape")+
  scale_fill_manual(name="Landscape", labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"), values = c("#a6cd5b", "#752559", "#72bad3", "#eb4024", "#a66f5b", "#449d8b", "#eb8932", "#2c6b96", "#e8af3c", "#9c8dc3"))+
  scale_x_discrete(expand=c(0.03,0))+
  scale_y_continuous(expand=c(0,0))

A_crops_grown

ggsave("A_crops_grown.png", plot = A_crops_grown, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 6, height = 4.5, units = c("in"),
  dpi = 300)

```

###Cause of Post-Harvest Food Loss
```{r}

A_food_loss <- 
  ggplot(filter(hh_fieldcrop, ag5a_21 != "NA", country == 'RWA'), aes(x= ag5a_21, fill=factor(landscape_no)))+
 geom_bar(stat = "count", position = 'stack')+
  theme_vsr()+
 theme(axis.text.x = element_text(angle = 90,  hjust = 1), plot.title = element_text(hjust = 0.5))+
 xlab ("Cause of Food Loss")+
 ylab("Number of Fields")+
 ggtitle("Cause of Post-Harvest Food Loss by Landscape")+
  scale_fill_manual(name="Landscape", labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"), values = c("#a6cd5b", "#752559", "#72bad3", "#eb4024", "#a66f5b", "#449d8b", "#eb8932", "#2c6b96", "#e8af3c", "#9c8dc3"))+
  scale_x_discrete(expand=c(0.03,0))+
  scale_y_continuous(expand=c(0,0))

A_food_loss

ggsave("A_food_loss.png", plot = A_food_loss, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 3.5, height = 4.5, units = c("in"),
  dpi = 300)

```

###Soil quality by landscape
```{r}
#Soil quality by landscape
A_soil_quality <- ggplot(data = filter(joined_df, ag3a_10 != "NA"), aes(landscape_no, fill=ordered(ag3a_10))) +
  geom_bar(stat="count", position = "fill")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
  xlab("Landscape")+
  ylab("Soil Quality (as reported by farmers)")+
  ggtitle("Soil Quality By Landscape")+
  scale_fill_manual(name="Soil Quality", labels =c("Good", "Average", "Bad"), values = c("#449d8b", "#e8af3c", "#eb4024"))  +
  theme_vsr()+
  scale_y_continuous(expand=c(0,0))

ggsave("A_soil_quality.png", plot = A_soil_quality, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 4.5, height = 3, units = c("in"),
  dpi = 300)
```

###Reason for Intercropping
```{r}
# Reason for intercropping
A_reason_inter <- ggplot(data=filter(joined_df, ag4a_05 != "NA"), aes(x=ag4a_05, fill=landscape_no))+
  geom_bar(stat="count")+
  xlab("Reason for Intercropping")+
  ylab("Count")+
  ggtitle("Household Survey of Reported Reasons for Intercropping")+
  scale_fill_manual(name="Landscape", labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"), values = c("#a6cd5b", "#752559", "#72bad3", "#eb4024", "#a66f5b", "#449d8b", "#eb8932", "#2c6b96", "#e8af3c", "#9c8dc3"))+
  scale_y_continuous(expand=c(0,0))+
  theme_vsr()

A_reason_inter

ggsave("A_reason_inter.png", plot = A_reason_inter, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 6, height = 3.5, units = c("in"),
  dpi = 300)

```





###Use of inputs by landscape and round

####Inorganic Fertilizer
```{r}

#.404686

A_crop_inorg_fert <- ggplot(data=joined_df, aes(x=ag3a_07_1, y=(ag3a_47/ag4a_08), fill=ag3a_46))+
  geom_bar(stat="identity")+
  xlab("Crop type")+
  ylab("Total amount of inorganic fertilizer applied (kg)")+
  ggtitle("Inorganic Fertilizer Use by Main Crop Type (Both Rounds)")+
  theme_vsr()+
  theme(axis.text.x = element_text(angle = 90, vjust = .4, hjust = 1))+
  scale_y_continuous(expand=c(0,0))+
  scale_fill_manual(name ="Fertilizer type", values = wes_palette("Darjeeling1"))

A_crop_inorg_fert

ggsave("A_crop_inorg_fert.png", plot = A_crop_inorg_fert, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 6.25, height = 4, units = c("in"),
  dpi = 300)


A_landscape_inorg_fert <- ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_47, fill=round))+
  geom_bar(stat="identity",position="stack")+
  xlab("Landscape")+
  ylab("Total amount of inorganic fertilizer applied (kg)")+
  ggtitle("Inorganic Fertilizer Use by Landscape and Round")+
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"))+
  theme_vsr()+
  scale_fill_manual(values =c("#72bad3", "#e8af3c"), name = "Round")

A_landscape_inorg_fert

ggsave("A_landscape_inorg_fert.png", plot = A_landscape_inorg_fert, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 4.5, height = 3.5, units = c("in"),
  dpi = 300)

```


####Organic Fertilizer
```{r}

A_crop_org_fert <- ggplot(data=joined_df, aes(x=ag3a_07_1, y=(ag3a_40/ag4a_08), fill=ag3a_39a))+
  geom_bar(stat="identity")+
  xlab("Crop type")+
  ylab("Total amount of organic fertilizer applied (kg)")+
  ggtitle("Organic Fertilizer Use by Main Crop Type (Both Rounds)")+
  theme_vsr()+
  theme(axis.text.x = element_text(angle = 90, vjust = .4, hjust = 1))+
  scale_y_continuous(expand=c(0,0))+
  scale_fill_manual(name ="Fertilizer type", values = wes_palette("Darjeeling1"))

A_crop_org_fert

ggsave("A_crop_org_fert.png", plot = A_crop_org_fert, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 5.7, height = 4, units = c("in"),
  dpi = 300)


A_landscape_org_fert <- ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_40, fill=round))+
  geom_bar(stat="identity",position="stack")+
  xlab("Landscape")+
  ylab("Total amount of organic fertilizer applied (kg)")+
  ggtitle("Organic Fertilizer Use by Landscape and Round")+
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"))+
  theme_vsr()+
  scale_fill_manual(values =c("#72bad3", "#e8af3c"), name = "Round")

A_landscape_org_fert

ggsave("A_landscape_org_fert.png", plot = A_landscape_org_fert, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 4.7, height = 3.5, units = c("in"),
  dpi = 300)

```

####Pesticides
```{r}

A_crop_pest <- ggplot(data=joined_df, aes(x=ag3a_07_1, y=(ag3a_60_1/ag4a_08), fill=ag3a_59))+
  geom_bar(stat="identity")+
  xlab("Crop type")+
  ylab("Total amount of pesticides applied (kg)")+
  ggtitle("Pesticide Use by Main Crop Type (Both Rounds)")+
  theme_vsr()+
  theme(axis.text.x = element_text(angle = 90, vjust = .4, hjust = 1))+
  scale_y_continuous(expand=c(0,0))+
  scale_fill_manual(name ="Pesticide type", values = wes_palette("Darjeeling1"))

A_crop_pest

ggsave("A_crop_pest.png", plot = A_crop_pest, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 5.25, height = 4, units = c("in"),
  dpi = 300)


A_landscape_pest <- ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_60_1, fill=round))+
  geom_bar(stat="identity",position="stack")+
  xlab("Landscape")+
  ylab("Total amount of pesticides applied (kg)")+
  ggtitle("Organic Fertilizer Use by Landscape and Round")+
  scale_y_continuous(expand=c(0,0))+
  scale_x_discrete(labels=c("1", "2", "3", "4", "6", "7", "8", "10", "11", "12"))+
  theme_vsr()+
  scale_fill_manual(values =c("#72bad3", "#e8af3c"), name = "Round")

A_landscape_pest

ggsave("A_landscape_pest.png", plot = A_landscape_pest, device = "png", path = "~/Documents/Bren/GP/3Graphs/Descriptives/",
  width = 4.5, height = 3.5, units = c("in"),
  dpi = 300)

```








######################










#a. PESTICIDE

Pesticide Use

#Explore pesticide use
```{r}

#Pesticide use (ag3a_58) (Yes/No) across everything
ggplot(data=joined_df, aes(ag3a_58))+
  geom_bar()+
  xlab("Was Any Pesticide/Herbicide Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Pesticides and Herbicides (All Landscapes/Rounds)")

```

#pesticide use (Yes/No) disaggregated by round
```{r}

#round 1
pesticide_r1 <- dplyr::filter(joined_df, round == "1")
ggplot(data=pesticide_r1, aes(ag3a_58))+
  geom_bar()+
  xlab("Was Any Pesticide/Herbicide Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Pesticides and Herbicides, Round 1 (All Landscapes)")

#round 2
pesticide_r2 <- dplyr::filter(joined_df, round == "2")
ggplot(data=pesticide_r2, aes(ag3a_58))+
  geom_bar()+
  xlab("Was Any Pesticide/Herbicide Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Pesticides and Herbicides, Round 2 (All Landscapes)")

#percentages of households using pesticide (total and by round)
table(joined_df$ag3a_58)
#F 2158 (%), T 216 (%)
table(round_1$ag3a_58)
#F 675 (%), T 103 (%)
table(round_2$ag3a_58)
#F 1483 (%), T 113 (%)

```

#explore types of pesticides used
```{r}

#total use of pesticide (Yes/No) by type 
ggplot(data=joined_df, aes(ag3a_59))+
  geom_bar()+
  xlab("Main type of pesticide/herbicide")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Types of Pesticides and Herbicides (All Landscapes/Rounds)")

#remove the NA's (people who did not use pesticide)
pesticide_sans_na <- dplyr::filter(joined_df, ag3a_59 != "na")

#total use of pesticide by type, minus NA's
ggplot(data=pesticide_sans_na, aes(ag3a_59))+
  geom_bar()+
  xlab("Main type of pesticide/herbicide")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Types of Pesticides and Herbicides (All Landscapes/Rounds)")

#conclusion: predominantly pesticides, little herbicide or fungicide
```

#explore the amount of pesticide used in kg
```{r}

#note some missing data for the amount of pesticide used

#####
#total amount of pesticide used in kg, by landscape and round
ggplot(data=joined_df, aes(x=landscape_no, y=pesticide_use_kg, fill=round))+
  geom_bar(stat="identity",position=position_dodge())+
  xlab("Landscape")+
  ylab("Amount of Pesticide Used (Kg)")+
  ggtitle("Use of Pesticide by Landscape and Round")

#Landscape 1 round 1 is so high due to 1 750kg entry. Might be an outlier, let's remove.
table(joined_df$pesticide_use_kg)
pesticide_outlier <- dplyr::filter(joined_df, pesticide_use_kg == "750")
pesticide_remove_outliers <- dplyr::filter(joined_df, pesticide_use_kg < 750)

#same graph, but with the outlier in landscape 1, round 1 removed
ggplot(data=pesticide_remove_outliers, aes(x=landscape_no, y=pesticide_use_kg, fill=round))+
  geom_bar(stat="identity",position=position_dodge())+
  xlab("Landscape")+
  ylab("Pesticide Use (Kg)")+
  ggtitle("Use of Pesticide by Landscape and Round (> 749 Kg Removed)")

```

#explore proportion of amount of pesticide used by type, landscape
```{r}

#proportion of different types of pesticide by landscape
ggplot(data=joined_df, aes(x=landscape_no, y=pesticide_use_kg, fill=ag3a_59))+
  geom_bar(stat="identity",position = "fill")+
  xlab("Landscape")+
  ylab("Proportion of Type of Pesticed Used")+
  ggtitle("Type of Pesticide by Landscape (Both Rounds)")

#same graph, outlier removed
ggplot(data=pesticide_remove_outliers, aes(x=landscape_no, y=pesticide_use_kg, fill=ag3a_59))+
  geom_bar(stat="identity",position = "fill")+
  xlab("Landscape")+
  ylab("Proportion of Type of Pesticed Used")+
  ggtitle("Type of Pesticide by Landscape (Both Rounds, Outlier Removed)")
```

#explore total pesticide used (kg) by main crop type
```{r}

#pesticide use (kg) by main crop type
ggplot(data=joined_df, aes(x=ag3a_07_1, y=pesticide_use_kg))+
  geom_bar(stat="identity")+
  xlab("Main Crop on Field")+
  ylab("Amount of Pesticide Used (All Types, Kg)")+
  ggtitle("Pesticide Use by Main Crop Type (Both Rounds)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#pesticide use by main crop type, pesticide type
ggplot(data=joined_df, aes(x=ag3a_07_1, y=pesticide_use_kg, fill=ag3a_59))+
  geom_bar(stat="identity")+
  xlab("Main Crop on Field")+
  ylab("Amount of Pesticide Used (Kg)")+
  ggtitle("Pesticide Use by Type and Main Crop Type (Both Rounds)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


#b. ORGANIC FERTILIZER


#explore fert use (Yes/No)
```{r}
##BOTH ROUNDS#####
table(joined_df$ag3a_39)
#did you use organic fertilizer on this field?
#40% False, 60% True

ggplot(data=joined_df, aes(ag3a_39))+
  geom_bar()+
  xlab("Was Any Organic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Organic Fertilizer (All Landscapes/Rounds)")

##ROUND 1#####
table(round_1$ag3a_39)
#did you use organic fertilizer on this field?
#42% False, 58% True

ggplot(data=round_1, aes(ag3a_39))+
  geom_bar()+
  xlab("Was Any Organic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Organic Fertilizer, Round 1 (All Landscapes)")

##ROUND 2#####
table(round_2$ag3a_39)
#did you use organic fertilizer on this field?
#40% False, 60% True

ggplot(data=round_2, aes(ag3a_39))+
  geom_bar()+
  xlab("Was Any Organic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Organic Fertilizer, Round 2 (All Landscapes)")

```

#explore types of org fert (ag3a_39a)
```{r}

#table of types of organic fertilizer
table(joined_df$ag3a_39a)
#Animal Manure: 97%

#Total use of organic fertilizer by type
ggplot(data=joined_df, aes(ag3a_39a))+
  geom_bar()+
  xlab("Main Source of Organic Fertilizer")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Source of Organic Fertilizer (All Landscapes/Rounds)")

```

#explore amount of org fert used (kg) 
```{r}

#total amount of fertilizer used in kg, by landscape and round
ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_40, fill=round))+
  geom_bar(stat="identity",position="stack")+
  xlab("Landscape")+
  ylab("Organic Fertilizer Use (Kg)")+
  ggtitle("Organic Fertilizer Use by Landscape and Round")+
  theme_vsr()

```

#explored amount of org fert used (kg) by crop
```{r fertilizer_by_main_crop}

#organic fertilizer used by main crop, organic fertilizer type
ggplot(data=joined_df, aes(x=ag3a_07_1, y=ag3a_40, fill=ag3a_39a))+
  geom_bar(stat="identity")+
  xlab("Main Crop on Field")+
  ylab("Amount of Organic Fertilizer Used (Kg)")+
  ggtitle("Organic Fertilizer Use by Main Crop Type (Both Rounds)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


#c. INORGANIC FERTILIZER


Explore use of inorganic fertilizer (Yes/No)
```{r}

table(joined_df$ag3a_45)
#17% used inorganic fertilizer (both rounds, all landscapes)

#Use of in-fert across all landscapes/rounds
ggplot(data=joined_df, aes(ag3a_45))+
  geom_bar()+
  xlab("Was Any Inorganic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Inorganic Fertilizer (All Landscapes/Rounds)")

### Use in round 1 ###

table(round_1$ag3a_45)
#16% used inorganic fert in round 1

ggplot(data=round_1, aes(ag3a_45))+
  geom_bar()+
  xlab("Was Any Inorganic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Inorganic Fertilizer, Round 1 (All Landscapes)")

### Use in round 2 ###

table(round_2$ag3a_45)
#18% used inorganic fert in round 2

ggplot(data=round_2, aes(ag3a_45))+
  geom_bar()+
  xlab("Was Any Inorganic Fertilizer Used On This Field?")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Inorganic Fertilizer, Round 2 (All Landscapes)")

### Mean amount of inorganic fertilizer used ###

mean(joined_df$ag3a_47, na.rm = TRUE)
#mean inorg fert used: 16 Kg

```

#Explore types of inorganic fertilizer
```{r}

#table of types of inorganic fertilizer
table(joined_df$ag3a_46)

#remove NA entries for infert
infert_type_df <- dplyr::filter(joined_df, ag3a_46 != "NA")

#plot types of infert
ggplot(data=infert_type_df, aes(ag3a_46))+
  geom_bar()+
  xlab("Main Type of Inorganic Fertilizer Used")+
  ylab("Number of Responses")+
  ggtitle("Total Use of Type of Inorganic Fertilizer (All Landscapes/Rounds)")+
  theme(axis.text.x = element_text(angle = 10, hjust = 1))

```

#Explore amount of inorganic fertilizer used by landscape and round
```{r}

#total amount of fertilizer used in kg, by landscape and round
ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_47, fill=round))+
  geom_bar(stat="identity",position="stack")+
  xlab("Landscape")+
  ylab("Inorganic Fertilizer Use (Kg)")+
  ggtitle("Inorganic Fertilizer Use by Landscape and Round")

#Proportion of type of inorganic fertilizer used by landscape
ggplot(data=joined_df, aes(x=landscape_no, y=ag3a_47, fill=ag3a_46))+
  geom_bar(stat="identity",position = "fill")+
  xlab("Landscape")+
  ylab("Proportion of Type of Inorganic Fertilizer Used")+
  ggtitle("Type of Inorganic Fertilizer by Landscape (Both Rounds)")

```

#Explore inorganic crop use by main crop type, fertilizer type
```{r}

ggplot(data=joined_df, aes(x=ag3a_07_1, y=ag3a_47, fill=ag3a_46))+
  geom_bar(stat="identity")+
  xlab("Main Crop on Field")+
  ylab("Amount of Inorganic Fertilizer Used (Kg)")+
  ggtitle("Inorganic Fertilizer Use by Main Crop Type (Both Rounds)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


#d. Quantity of Crop Harvest


```{r}

#Sum kg for crops 
totalharvest_graph <- aggregate(ag4a_15 ~ crop_name, fieldcrop, sum) 
area_harvestgraph <- aggregate(kg_perha_planted ~ crop_name, joined_df, sum)

#Quantity of Crop Harvest (kg)
ggplot(totalharvest_graph, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest (kg)")

#Quantity of Harvest by kg/Hectare
ggplot(area_harvestgraph, aes(x= crop_name, y= kg_perha_planted))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
  xlab("Crop Name")+
  ylab("Kilograms of Harvest per Hectare Planted")+
  ggtitle("Quantity of Crop Harvest (kg/hectare planted)")

#Count of Total Crop Harvest by Landscape
ggplot(fieldcrop, aes(x= crop_name, fill=factor(landscape_no)))+
 geom_bar(stat = "count", position = 'stack')+
 theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
 xlab ("Crop")+
 ylab("Total Harvest (kg)")+
 ggtitle("Quantity of Total Crop Harvest by Landscape")+
  scale_fill_discrete(name = "Landscape",
labels = c("Nyungwe", "Volcanoes", "Akagera", "Gishwati", "Muhanga-Kamonyi", "Bugesera"))

#Crop Yield by Landscape (kg/hectare planted)
ggplot(joined_df, aes(x= crop_name, y= kg_perha_planted, fill=factor(landscape_no)))+
 geom_bar(stat = "identity", position = 'stack')+
 theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
 xlab ("Crop")+
 ylab("Yield of Harvest (kg/ha planted)")+
 ggtitle("Yield by Crop Type")+
  scale_fill_discrete(name = "Landscape",
labels = c("Nyungwe", "Volcanoes", "Akagera", "Gishwati", "Muhanga-Kamonyi", "Bugesera"))

#Isolate landscape dfs and make graphs by landscape. Both rounds included in these graphs
fieldcrop_L01 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L01')
fieldcrop_L02 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L02')
fieldcrop_L03 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L03')
fieldcrop_L04 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L04')
fieldcrop_L06 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L06')
fieldcrop_L07 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L07')
fieldcrop_L08 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L08')
fieldcrop_L10 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L10')
fieldcrop_L11 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L11')
fieldcrop_L12 <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15_unit == 'Kg', ag4a_15 != "na", landscape_no =='L12')

totalharvest_L01 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L01, sum) # sum kg for crops 
totalharvest_L02 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L02, sum) # sum kg for crops 
totalharvest_L03 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L03, sum) # sum kg for crops 
totalharvest_L04 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L04, sum) # sum kg for crops 
totalharvest_L06 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L06, sum) # sum kg for crops 
totalharvest_L07 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L07, sum) # sum kg for crops 
totalharvest_L08 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L08, sum) # sum kg for crops 
totalharvest_L10 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L10, sum) # sum kg for crops 
totalharvest_L11 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L11, sum) # sum kg for crops 
totalharvest_L12 <- aggregate(ag4a_15 ~ crop_name, fieldcrop_L12, sum) # sum kg for crops 

#Quantity of harvest by landscape
ggplot(totalharvest_L01, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Nyungwe")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L02, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Volcanoes")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L03, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Akagera")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L04, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Gishwati")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L06, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Muhanga-Kamonyi")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L07, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for Bugesera")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L08, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for L08")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L10, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for L10")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L11, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for L11")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

ggplot(totalharvest_L12, aes(x= crop_name, y= ag4a_15))+
  geom_bar(stat = "identity")+
  xlab ("Crop")+
  ylab("Total Harvest (kg)")+
  ggtitle("Quantity of Crop Harvest for L12")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))


```


#e. Reason for Intercropping


```{r}

library(RColorBrewer)


  
ggplot(data=filter(joined_df, ag4a_05 != "NA"), aes(x=ag4a_05))+
  geom_bar(stat="count")+
  xlab("Reason for Intercropping")+
  ylab("Frequency")+
  ggtitle("Household Survey of Reported Reasons for Intercropping")+
  scale_fill_manual(values=c("firebrick1", "darkorange", "deepskyblue3"))+
  theme_minimal()

plot

#ag4a_05 - What is the reason for this intercropping?

```


#f. Soil Quality


```{r}

#intercrop subset
jdf_intercrop <- filter(joined_df, crop_name == "Irish Potatoes" | crop_name == "Maize" | crop_name == "Sorghum" | crop_name == "Sweet Potatoes" | crop_name == "Banana Beer" | crop_name == "Banana Food" | crop_name == "Beans" | crop_name == "Field Peas")

#Soil quality as a function of intercropping
ggplot(data = filter(jdf_intercrop, ag3a_10 != "NA"), aes(ag4a_04, fill=ordered(ag3a_10, levels=c("Good", "Average", "Bad")))) +
  geom_bar(stat="count", position = "fill")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
  xlab("Plot Was Intercropped?")+
  ylab("Soil Quality (as reported by farmers)")+
  ggtitle("Soil Quality as a Function of Intercropping")+
  scale_fill_discrete(name="Soil Quality", labels =c("Good", "Average", "Bad"))

#Soil quality by landscape
ggplot(data = filter(joined_df, ag3a_10 != "NA"), aes(landscape_no, fill=ordered(ag3a_10))) +
  geom_bar(stat="count", position = "fill")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
  xlab("Landscape")+
  ylab("Soil Quality (as reported by farmers)")+
  ggtitle("Soil Quality By Landscape")+
  scale_fill_discrete(name="Soil Quality", labels =c("Good", "Average", "Bad"))  

```


#g. Crop residue use


```{r}
#Crop residue use in Rwanda
ggplot(filter(hh_fieldcrop, country == 'RWA', ag5a_24 != "NA"), aes(ag5a_24)) + geom_histogram(stat = "count", bins = 20) +
 ggtitle("Crop residue use") + theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

#Crop residue use as a function of country
ggplot(filter(hh_fieldcrop, ag5a_24 != "NA"), aes(ag5a_24)) + geom_histogram(stat = "count", bins = 20) +
 ggtitle("Crop residue use") + theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+facet_grid(.~country)

#Crop residue use by landscape in Rwanda
ggplot(filter(hh_fieldcrop, country == 'RWA', ag5a_24 != "NA"), aes(x= ag5a_24, fill=factor(landscape_no)))+
 geom_bar(stat = "count", position = 'stack')+
  theme_classic()+
 theme(axis.text.x = element_text(angle = 60,  hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
 xlab ("Crop residue use")+
 ylab("Count")+
 ggtitle("Crop residue use by Landscape")+
  scale_fill_discrete(name = "Landscape")

```


#h. Food Loss


```{r}

#histogram food loss in Rwanda
ggplot(filter(hh_fieldcrop, ag5a_21 != "NA", country == 'RWA'), aes(ag5a_21)) + geom_histogram(stat = "count", bins = 20) +
 ggtitle("Cause of Food Loss") + theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))

#histogram food loss ~ country
ggplot(filter(hh_fieldcrop, ag5a_21 != "NA"), aes(ag5a_21)) + geom_histogram(stat = "count", bins = 20) +
 ggtitle("Cause of Food Loss") + theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+facet_grid(.~country)

#histogram food loss ~ landscape
ggplot(filter(hh_fieldcrop, ag5a_21 != "NA", country == 'RWA'), aes(ag5a_21)) + geom_histogram(stat = "count", bins = 20) +
 ggtitle("Cause of Food Loss") + theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust=.3), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+facet_grid(.~landscape_no)

#stacked bar graph food loss ~ landscape
ggplot(filter(hh_fieldcrop, ag5a_21 != "NA", country == 'RWA'), aes(x= ag5a_21, fill=factor(landscape_no)))+
 geom_bar(stat = "count", position = 'stack')+
  theme_classic()+
 theme(axis.text.x = element_text(angle = 45,  hjust = 1), plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
 xlab ("Cause of Food Loss")+
 ylab("Count")+
 ggtitle("Cause of Post-Harvest Food Loss by Landscape")+
  scale_fill_discrete(name = "Landscape")

#stacked bar graph food loss ~ country
ggplot(filter(hh_fieldcrop, ag5a_21 != "NA"), aes(country, fill=ordered(ag5a_21))) +
  geom_bar(stat="count", position = "fill")+
  theme(plot.title = element_text(hjust = 0.5, face="bold"), legend.title=element_text(face="bold"), axis.title=element_text(face="bold"))+
  xlab("Country")+
  ylab("Percentage of Total Loss")+
  ggtitle("Cause of Post-Harvest Food Loss by Country")+
  scale_fill_discrete(name="Cause of Food Loss")

```

